Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-11 WSSSPE4_report/WSSSPE4_report.tex
add group formation process

Intro and description \katznote{not sure enum list is right here}
%
\begin{enumerate}
\item \textbf{Authors: \emph{title}}.
Description

\end{enumerate}

@@

\todo{describe process for assembling people into working groups: vision, gaps, projects exercise, then soapboxes}

@@

As part of the discussion at WSSSPE4, we created a Slack team for WSSSPE.  To join it, go to \url{https://wssspe.signup.team/}.  A number of the working groups also created channels within the team; see the subsections in \S\ref{sec:WGs} for the names of these channels.

>>>>

Intro and description 
%
\begin{itemize}
\item \textbf{Authors: \emph{title}}.
Description

@@

After most of the lightning talks and other presentations, WSSSPE used three areas of a large room to let
attendees use sticky flip charts and sticky notes on the walls to suggest 
\begin{enumerate}
\item A vision on any aspect of the work.
\item A gap or challenge
\item A project idea
\end{enumerate}
(with one area of the room for each topic.)

Once we had the walls covered in ideas, we had people organically form groups around the flip charts on the wall. \todo{find photos of flip charts, put in repo?} We asked them to work in Google Docs, \todo{find and cite these docs?} using a template for Vision, Gaps, and Projects.  For those folk who worked on Vision and Gaps, after an hour, we encouraged them to finish their Vision or Gap Google Doc, and to find and join or start working on a project with a group. This led to the 12 groups that are discussed in the rest of this section, specifically:
\begin{enumerate}
\item Verifying best practices \& metrics for sustainable research software
\item Software Sustainability Alliance
\item Scientific Software Prototyping Infrastructure (S2PI)
\item Standard metadata for software (CodeMeta)
\item White paper on developing sustainable software
\item Social science for scientific software
\item Software best practices for undergraduates
\item Meaningful metrics for sustainable software
\item Coordinating access to CI for research software
\item Software engineering processes tailored for research software
\item Open research index
\item Letters of evaluation for computational scientists
\end{enumerate}

@@

As part of the discussion at WSSSPE4, we created a Slack team for WSSSPE~\cite{WSSSPESlack}.  To join it, go to \url{https://wssspe.signup.team/}.  A number of the working groups also created channels within the team; see the subsections in \S\ref{sec:WGs} for the names of these channels.
